\documentclass[a4paper,12pt,twoside]{report}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=3cm]{geometry}

\include{preamble}

\title{\LARGE {A numerical investigation of hydrocarbon related magnetic signatures}\\
\vspace*{6mm}
}

\author{Miguel A. Valdez Grijalva}

\raggedbottom

\begin{document}
\pagestyle{fancy}
\maketitle

\pagenumbering{arabic}
\setcounter{page}{2}

\include{pre/declarations}
\include{pre/abstract}
\include{pre/acknowledgements}
\include{pre/dedication}
\include{pre/quote}
\include{pre/nomenclature}
\pagestyle{plain}

%\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Contents}
\tableofcontents
\newpage
%\listoftables

\phantomsection
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures

\newpage
\phantomsection
\addcontentsline{toc}{chapter}{List of Publications}
\chapter*{List of Publications}
Valdez-Grijalva, M. A., Nagy, L., Muxworthy, A. R., Williams, W., Fabian, K., 2018. The magnetic structure and palaeomagnetic recording fidelity of sub-micron greigite (Fe$_3$S$_4$). Earth Planet. Sci. Lett. 483, 76--89.\par
\bigskip
\noindent Valdez-Grijalva, M. A., Muxworthy, A. R., 2018. First-order reversal curve (FORC) diagrams of nanomagnets with cubic magnetocrystalline anisotropy. J. Magn. Magn. Mater., in review.\par
\bigskip
\noindent Valdez-Grijalva, M. A., Muxworthy, A. R., Williams, W., \'O Conbhu\'i, P., Nagy, L., Roberts, A. P., Heslop, D., 2018. Magnetic vortex effects on first-order reversal curve (FORC) diagrams for greigite dispersions. Earth Planet. Sci. Lett., in review.\par

\printnomenclature

\fancyhead[L]{\leftmark}
\fancyhead[C]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\thispagestyle{empty}
\pagestyle{fancy}

\doublespacing
%\linespread{1.5}
\clearpage

%\setcounter{page}{1}
%\pagenumbering{arabic}

%\include{intro/intro}
%\include{research-1/research-1}
%\include{research-2/research-2}
%\include{research-3/research-3}
%\include{research-4/research-4}
%\include{conclusions/conclusions}

\input{intro/intro}
\input{research-1/research-1}
\input{research-2/research-2}
\input{research-3/research-3}
\input{research-4/research-4}
\input{conclusions/conclusions}


%\newpage
%\begin{finalreferences}
%\let\cleardoublepage\clearpage
%\addcontentsline{toc}{chapter}{References}
\chapter*{References}
\fancyhead[L]{References}
\fancyhead[C]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}
\pagestyle{fancy}
%\thispagestyle{empty}
\addcontentsline{toc}{chapter}{References}
\renewcommand\bibname{{}}
\bibliographystyle{elsarticle-harv}
\bibliography{references}
%\end{finalreferences}
\appendix
\include{appendix/appendix}
%\include{}

\end{document}
