\let\cleardoublepage\clearpage
%\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}

\begin{acknowledgements}
I would like to thank all the people who contributed in some way to the completion of this thesis. I thank my academic advisor, Dr. Adrian Muxworthy, for accepting me into his research group. During my time in the Natural Magnetism group he contributed to a rewarding graduate school experience by giving me intellectual freedom to pursue my research, supporting me to participate in various conferences, motivating research directions and always demanding high-quality work. I would also like to thank Prof. Wyn Williams for co-advising my work and very engaging conversations on micromagnetic modelling applied to Earth Science. This adventure would not have been possible without the trust of my sponsors, Instituto Mexicano del Petr\'oleo and especially Dr. Aleksandr Mousatov, who always supported my work.\par

I thank Les Nagy and P\'adraig \'O Conbhu\'i for getting me up to speed with the micromagnetic code used in this thesis and for very interesting conversations on many topics. The pain of compiling software on HPCs was always attenuated by their insight. I am grateful to Prof. Andrew Roberts and Dr. David Heslop for allowing me access and computing time in Terrawulf and for their very insightful observations to my simulations.\par

I would like to show my gratitude to Thomas Berndt and Jay Shah for making me feel at home in the group when I first started and for conversations that led to ideas and collaborations. I would also like to thank Aike Supakulopas, Sope Badejo, Charlie Penny and Rabiu Abubakar for sharing their work with me, which led me to a broader understanding of palaeomagnetism and rock magnetism.\par

I owe my gratitude to Shahar and Gemma, without their friendship London would have been much colder. I also thank Den\'i, Matt, Duna, Thibaut, Rodolfo, Mossayeb, Laura and Jiangang for their camaraderie; my time at Imperial College would not have been as interesting and pleasurable without them.\par

I thank my parents, Gabriela and Miguel, for supporting me always. Your love and dedication inspired me throughout this time.\par

Last but not least, I thank Isabel. I could not have finished this work without her. Her love and unwavering support helped me in the most difficult times. Her resilience always inspired me not to give up. She gave me eyes to see the world in ways I never knew. I am eternally grateful to you.\par
\end{acknowledgements}
