\chapter{Conclusions}
\label{ch:conclusions}
\fancyhead[L]{Chapter 6. Conclusions}
\fancyhead[C]{}
\fancyhead[R]{}
\fancyfoot[C]{\thepage}

\section{Numerical models and greigite}
Numerical methods have been employed to answer some open questions about the magnetic properties of rocks containing the ferrimagnetic mineral greigite. Difficulty in producing pure greigite with well-constrained sizes and morphologies makes numerical methods the best option for studying the magnetic hysteresis properties and thermal stability of this mineral.\par

In this study, the focus was first on the zero-field magnetic structures and the stability of these against thermal fluctuations (Chapter \ref{ch:res-1}) via micromagnetic methods. This has allowed me to determine precisely the single-domain (SD) to pseudo single-domain (PSD) threshold and the room temperature blocking volumes for a variety of naturally occurring shapes.\par

A simplified model for hysteresis of SD, coherently rotating particles with cubic magnetocrystalline anisotropy (MCA) was developed (Chapter \ref{ch:res-2}). This method allows for fast calculations of hysteresis loops and first-order reversal curve (FORC) diagrams for non-interacting ensembles of cubic anisotropic minerals. To my knowledge, this simplified model for cubic MCA is the first of its type (energy minimisation-based).\par

Hysteresis and FORC diagram properties of non-interacting SD and SV particle dispersions have been calculated with a micromagnetic method \citep{OConbhui2017} (Chapter \ref{ch:res-3}). This has allowed for a robust reinterpretation of the FORC diagram for SV particles. The FORC properties of highly-interacting framboidal greigite dispersions have been calculated with a micromagnetic method \citep{OConbhui2017} (Chapter \ref{ch:res-4}).\par

\subsection{Basic zero-field properties}
Zero-field structures were found to be highly shape- and size- dependent (Chapter \ref{ch:res-1}). The magnetic free-energy of the different domain states like the SD state and the differently aligned SV states was determined as a function of shape and size. A plausible mechanism for a SD--MD transition was identified. This proceeds by the growth of particles in an easy aligned SV state. As the particle grows, the magnetic vortex regions aligned closely with easy axes grow, while the rest of the regions become more domain-wall-like.\par

A nudged elastic-band method \citep{Fabian2017} was used to determine the energy barriers between the minimal-energy states as a function of particle size and shape. This allowed me to determine precisely the shape dependency of the SD--PSD threshold, $d_0\approx 54 \nm$ for truncated-octahedral particles (the most common natural greigite shape) and the room temperature blocking volumes of sub-micron greigite for different naturally occurring shapes, $\roughly$74$\nm$ for truncated-octahedral particles. It was found that isolated SD greigite is essentially super-paramagnetic and only larger particles $d>\roughly$74$\nm$ SV grains can carry stable magnetisations over geological scales.\par

Uncertainty in the measured value of $A$ \citep{Chang2008} for greigite is hard to quantify in absence of other measurements obtained via different methods to compare with. Based on the lower bound for the Curie temperature of greigite $T_\text{C} > 620\,\text{K}$ \citep{Roberts2011}, the value of $A$ could be up to $\roughly$4 times higher. Using values for $A$ twice ($A=4\times 10^{-12}\,\text{J}/\text{m}^3$) and four times ($A=8\times 10^{-12}\,\text{J}/\text{m}^3$) larger I re-calculated the SD--SV threshold $d_0$ for a truncated-octahedral particle. Increasing $A$ increases $d_0$ from $\roughly 54\nm$ to $\roughly 62\nm$ for $A=4\times 10^{-12}\,\text{J}/\text{m}^3$ and up to $\roughly 90\nm$ for $A=8\times 10^{-12}\,\text{J}/\text{m}^3$. This would imply that the blocking volume would also shift to larger values. However, the general behaviour, i.e., low energy barriers for transitions between SD states making equidimensional SD greigite essentially SP and only larger SV grains holding stable magnetisations over geological timescales, would remain the same. This is supported by the same behaviour being observed in simulations for equidimensional iron \citep{Shah2018} particles, which have a very different set of magnetic parameters.\par

\subsection{Hysteretic and FORC properties}
The FORC properties of non-interacting dispersions of ideal SD grains with cubic MCA were investigated with a novel algorithm based on energy minimisation of the energy of an idealised SD coherently rotating particle (Chapter \ref{ch:res-2}). The method proposed in this study is fast and found to be as accurate as micromagnetic models of small SD particles for which the effects of non-uniform magnetisations are negligible. Characteristic FORC signals were determined for SD particles with cubic MCA. A tilted, elongated, negative ridge was identified as the magnetic signature of non-interacting SD particles with multi-axial MCA (Fig. \ref{FIG_E04}).\par

Both the dipolar (Chapter \ref{ch:res-2}) and the full micromagnetic (Chapter \ref{ch:res-3}) models predict a coercivity $B_\text{C}\approx 24\mT$ much lower than the widely recognised $B_\text{C}\approx 60\mT$ in natural greigite samples \citep{Roberts2011}. This could be explained by either: a) the measured (absolute) value of $K_1$ \citep{Winklhofer2014} is significantly lower than its real value; b) particle elongations produce a shape (uniaxial) anisotropy which increases the coercivities of natural samples; c) magnetostrictive effects play an important role in natural greigite or d) a combination of these effects. Natural greigite is commonly identified by concentric FORC diagram contours centered around $B_c\approx 60\mT$, usually unaccompanied by the negative-valued ridge identified for non-uniaxial SD particles. This lends more credibility to the relatively high coercivities of natural greigite samples being explained by some physical mechanism conducive to the formation of an effective uniaxial MCA. However, it is also possible that relatively weak interparticle magnetostatic interactions can cause the negative ridge to disappear, while also producing the vertical spread commonly observed in greigite FORC diagrams. More research is necessary to solve this apparent paradox.\par

To go beyond idealised magnetic domain states and reversal mechanisms, a micromagnetic algorithm was used to calculate the FORC properties of non-interacting dispersions of greigite in the SD to SV size range (Chapter \ref{ch:res-3}). SV effects and their onset were precisely identified. On increasing particle size within the model, these are apparent from 50$\nm$, slightly below the zero-field SD--PSD threshold (here calculated to be $d_0\approx 54\nm$) and completely dominant from 76$\nm$. SV particles produce FORC diagrams very different from SD particles (Fig. \ref{FIG_C4_07}). Also, it was shown that the interpretation of the FORC diagram should be domain state-dependent, i.e., FORC diagrams for SD particles provide a coercivity distribution whereas for SV particles, the FORC responses are mostly associated with vortex nucleation and annihilation fields as observed by \citep{Pike1999B} for nano-patterned synthetic arrays.\par

Since greigite rarely occurs naturally as isolated particles, a micromagnetic algorithm was used to calculate the FORC response of an ensemble of randomly dispersed greigite framboids. The magnetic signature of these framboids was found to be like that of MD particles. Most naturally occurring greigite is found as a fine-grained phase; therefore, samples known to contain greigite that produce MD-like FORC diagrams should be interpreted as containing framboidal or some other form of strongly interacting greigite.\par

The FORC signal of SD greigite is commonly assumed to be concentric contours with a relatively high coercivity despite, being observed to occur in tight clusters. According to the simulations presented in this study, strong magnetostatic interactions between the particles expected to exist in tight clusters should make the FORC signal more similar to a low coercivity MD response. Given the metastable nature of greigite, it is possible that pyritisation of the greigite surfaces causes the effective distance between the magnetic grains of greigite to increase, reducing the magnetic interactions between the particles. This is supported by samples from Taiwan \citep{Chou2012}, known for their high content of greigite, having FORC responses similar to the framboidal signal simulated here (Fig. \ref{FIG_F06_Chou2012}). Whereas, samples from New Zealand marine sediments known to have undergone extensive pyritisation \citep{Rowan2006} have concentric contours (Fig. \ref{FIG_F06_Rowan2006}). A thorough investigation of the transition from a non-interacting to a strongly interacting regime is still needed.\par

\section{Future work}
Memory and time constraints imposed by the available computing facilities (Imperial College's high-performance cluster (HPC) CX1 (Chapter \ref{ch:res-3}) and Australia National University's HPC Terrawulf (Chapter \ref{ch:res-4})) have restrained some aspects of this investigation. Future studies need to focus on simulations of FORC properties for larger non-interacting grains to determine the onset of MD behaviour. The largest particle size studied here was 80$\nm$. Based on extrapolations, it is possible that already at $\roughly$90$\nm$ the $B_\text{CR}/B_\text{C}$ ratio is as large as 4 and $M_\text{RS}/M_\text{S}$ as low as 0.05; this would be a Day plot region commonly identified as MD (for uniaxial particles). This would lend more credibility to the theory of MD formation elaborated in this study, i.e., SV particles are essentially MD.\par

Larger grains in larger framboids (composed of more particles) also need more investigation. However, it is most likely that their FORC responses will be even more MD-like. If a framboid composed of particles as small as 30$\nm$ produces MD-like signals, it is logical to expect larger grains to produce MD-like signals. Perhaps it will be of greater interest to attempt nudged elastic-band studies of framboidal greigite and determine their stability as a palaeomagnetic recorder. It would be very illuminating, but challenging, to include nudged elastic-band calculations to hysteresis and FORC simulations to obtain temperature-dependent properties. Nudged elastic-band methods couls also be used to investigate the super-paramagnetic to SD threshold in framboidal clusters. Another interesting area is to investigate the dynamic interactions of the crystallites in the framboids. However, simulations using LLG equation solvers are needed for this, which are orders of magnitude slower than energy minimisers and so are impossible at this stage. The FORC properties of magnetite framboids need investigating, although it is very likely they will be found to produce MD-like FORC signals. It would be very interesting to compare micromagnetic simulations to electron holography images like \citet{Einsle2016} did for iron particles in dusty olivines. This is very difficult, however, due to gregite's chemical instability.\par

The studies presented here and these further avenues for research could eventually be integrated to magnetic hydrocarbon explorations and environmental magnetic studies. Current research suggests that hydrocarbon migration produces more iron sulphides while depleting the iron oxide content of the host rocks. Results of this work can aid a robust proxy for identifying iron sulphides via bulk rock magnetic measurements and prove a valuable tool in the search for hydrocarbons as this non-renewable resource becomes ever scarcer.\par

%----------------------------------
%\renewcommand\bibname{{References}}
%\bibliographystyle{elsarticle-harv}
%\bibliography{references}

